---
title: "string_practice"
author: "Javier Patron"
date: "2022-08-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 3

```{r}
alarm_report <- tibble::tribble(
         ~date,           ~building,                                              ~alarm_message,
  "2020-03-14", "Engineering-North", "10:02am – HVAC system down, facilities management alerted",
  "2020-03-15",         "Bren Hall",                    "8:24am – Elevator North out of service",
  "2020-04-10", "Engineering-South",     "12:41am – Fire alarm, UCSB fire responded and cleared",
  "2020-04-18",        "Engr-North",     "9:58pm – Campus point emergency siren, UCPD responded"
  )

```

-   Replace the \"Engr\" with \"Engineering\" in the `building` column

```{r}
str_alarm_report <- alarm_report |> 
  mutate(building = str_replace(building, pattern = "Engineering", replacement = "Engr")) |> 
  separate(col = building, into = c("building", "wing"), sep = c("-")) |> 
  filter(str_detect(alarm_message, "responded")) |> 
  separate(alarm_message, into = "time", sep = ("—")) |> 
  mutate(date = lubridate::ymd(date))

class(str_alarm_report$date)
```

-   Separate the `building` column into two separate columns, `building` and `wing`, separated at the dash

-   Only keep observations with the word \"responded\" in the `alarm_message` column

-   Separate the message *time* from the rest of the message by separating at `--`

-   Convert the date column to a Date class using `lubridate`
